%====================
% EXPERIENCE A
%====================
\subsection{{ETL Automation \& Data Migration \hfill July 2023 -- June 2024}}
\subtext{Micron Technologies \hfill Hyd, Telangana}
\begin{zitemize}
\item Automated manual DDL rewriting and ETL migration from MSSQL, Oracle, and SAP HANA to Snowflake, drastically reducing manual effort and errors.
\item Developed robust Python scripts with comprehensive logging and error-handling, standardizing data workflows and improving overall deployment speed.
\item Automated synchronization of DDL changes across development, test, and production environments, significantly minimizing downtime and ensuring consistent deployment.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{NPI Sales Order Pipeline \hfill July 2024 -- Nov 2024}}
\subtext{Micron Technologies \hfill Hyd, Telangana}
\begin{zitemize}
\item Engineered an end-to-end automated pipeline to validate process codes and verify product availability, replacing time-consuming manual processes.
\item Leveraged Snowflake and GCP Scheduler to streamline data processing, significantly shortening the turnaround time for inventory checks and order validations.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Utility Trade Reports (UTR) Pipeline \hfill Dec 2024 -- Present}}
\subtext{Micron Technologies \hfill Hyd, Telangana}
\begin{zitemize}
\item Designed an efficient pipeline that converts raw fab data into actionable utility trade ratios, reducing report generation time and manual intervention.
\item Utilized GCP services (Cloud Functions, BigQuery, Pub/Sub, Workflows) and FastAPI to deliver real-time insights, ensuring rapid and reliable data access for manufacturing decisions.
\item Implemented automated data validation and error-handling measures, enhancing data integrity and reducing downstream processing delays.
\item Optimized SQL stored procedures and scheduling processes to significantly reduce report generation times and manual intervention.
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Advanced Automation \& AI Integration}}
\subtext{Micron Technologies \hfill Hyd, Telangana}
\begin{zitemize}
\item Integrated parallel processing with Ray to accelerate large-scale ETL operations, dramatically cutting overall processing times.
\item Deployed generative AI workflows using LLMs and RAG-based systems to automate routine tasks, further enhancing pipeline efficiency.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}
